Improving the modelling of tempo and phoneme duration

### 2017-02-19 Paper/Paper_v1.tex
py-files for error calculation and some minor changes to the others.
Syllable counter in pyfiles and some new weka files as text-file

@@

\chapter{Conclusion and Outlook}
Analyze duration changes of vowels in interrupted words.

>>>>

Long a shows a strong negative correlation with the local speech rate for secondary stressed and unstressed instances.

@@

\chapter{Conclusion and Outlook}
Analyze duration changes of vowels in interrupted words.
Consider actual realized syllables in speech instead of syllables based on the canonical transcription. In spontaneous speech, the word and syllable boundaries change, and this change influences other phonetic aspects such as stress, syllable duration, phoneme duration.
